analysing results

### 2022-11-16 manuscript/03-experiment.qmd
Cleaner code

library(ggraph)
library(igraph)
library(tidyverse)

data <- data.frame(
  level1="Total",
  level2=c("Central & West", "Central & West","Central & West","North", "South & East","South & East","South & East"),
  level3=c("HD", "SB", "PO", "BC","CV", "CT", "AB")
)
# transform it to a edge list!
edges_level1_2 = data %>% select(level1, level2) %>% 
  unique %>% rename(from=level1, to=level2)
edges_level2_3 = data %>% select(level2, level3) %>% 
  unique %>% rename(from=level2, to=level3)
edge_list=rbind(edges_level1_2, edges_level2_3)

mygraph <- graph_from_data_frame( edge_list )
ggraph(mygraph, layout = 'dendrogram', circular = FALSE) + 
  geom_edge_diagonal() +
  geom_node_point(colour="#dddddd",size=10) +
  geom_node_text(
    aes(label=c("All country", "Central & West", "North","South & East", "HD", "SB", "PO", "BC","CV", "CT", "AB") )
  )+
  theme_void()

@@

```{r}
#| label: tbl-hierarchy
#| tbl-cap: "Number of time series in each level for the hierarchical & grouped structure of attended incidents"
agg_level <- tibble::tribble(
  ~Level, ~`Number of series`,
  "All country", 1,
  "Control", 3,
  "Health board", 7,
  "Priority", 3,
  "Priority * Control", 9,
  "Priority * Health board", 21,
  "Nature of incident", 35,
  "Nature of incident * Control", 105,
  "Nature of incident * Health board", 245,
  "Priority * Nature of incident", 104,
  "Control * Priority * Nature of incident", 306,
  "Control * Health board * Priority * Nature of incident (Bottom level)", 691,
  "Total", 1530
)
knitr::kable(agg_level, booktabs = T, position = "left") %>% kable_classic(full_width = F)
```

@@

```{r}
#| label: fig-feature
#| cache: true
#| out.width: "70%"
#| fig.align: center
#| fig-cap: "Time series features of attended incidents across all levels (1530 series)"
library(feasts)
incident_gthf <- read_rds(paste0(storage_folder, "incidents_gt.rds"))
incident_gthf <- read_rds(here::here("data/incident_gt.rds"))
incident_gthf %>% 
  features(incident,feat_stl) %>%
  ggplot(aes(x = trend_strength, y = seasonal_strength_week)) +
  geom_point(pch=1)+
  ggthemes::theme_few()
```

@@

```{r}
#| label: fig-dataviz
#| cache: true
#| dependson: "fig-feature"
#| out.width: "70%"
#| fig-cap: "Time series of attended incidents at various levels"
#| fig-subcap: 
#|   - "all country"
#|   - "Control area"
#|   - "Health board and control area"
#|   - "Healthboard and priority"
#|   - "Nature of incident and health board"
#| layout: [[44,-2, 44], [44,-2, 44], [100]]
p_total <- incident_gthf %>%
    filter(is_aggregated(region) & is_aggregated(lhb) & is_aggregated(category) & is_aggregated(nature)) %>%
    autoplot()+
    labs(x="Date", y="Incidents")+
    ggthemes::theme_few()

p_total_control <- incident_gthf %>%
  filter(!is_aggregated(region) & !is_aggregated(lhb) & is_aggregated(category) & is_aggregated(nature)) %>%
  as_tibble() %>% select(-nature,-category) %>% 
  group_by(date,region) %>% summarise(incidents=sum(incidents), .groups="drop") %>% 
  ggplot(aes(x=date, y= incidents, colour = factor(region))) +
  geom_line()+
  labs(x="Date", y="Incidents", colour = "Control")+
  ggthemes::scale_color_colorblind()+
  ggthemes::theme_few()+
  theme(legend.position = "bottom")

p_control <- incident_gthf %>%
  filter(!is_aggregated(region) & !is_aggregated(lhb) & is_aggregated(category) & is_aggregated(nature)) %>%
  as_tibble() %>% select(-nature,-category) %>% 
  ggplot(aes(x=date, y= incidents, colour = factor(lhb))) +
  geom_line()+
  facet_wrap(vars(factor(region)), scales = "free_y")+
  labs(x="Date", y="Incidents", colour = "Health board")+
  ggthemes::scale_color_colorblind()+
  ggthemes::theme_few()+
  theme(legend.position = "bottom")

p_priority <- incident_gthf %>%
  filter(!is_aggregated(region) & !is_aggregated(lhb) & !is_aggregated(category) & is_aggregated(nature)) %>%
  as_tibble() %>% select(-nature,-region) %>% 
  ggplot(aes(x=date, y= incidents, colour = factor(lhb))) +
  geom_line()+
  facet_wrap(vars(factor(category)), scales = "free_y")+
  labs(x="Date", y="Incidents", colour = "Health board")+
  ggthemes::scale_color_colorblind()+
  ggthemes::theme_few()+
  theme(legend.position = "bottom")

@@

p_nature_healthboard <- incident_gthf %>%
  filter(!is_aggregated(region) & !is_aggregated(lhb) & !is_aggregated(category) & !is_aggregated(nature)) %>% 
as_tibble() %>% mutate(nature=as.character(nature)) %>% 
  filter(nature %in% selected_nature) %>% group_by(date,nature,lhb) %>% summarise(incidents=sum(incidents), .groups="drop") %>% 
  ggplot(aes(x=date, y= incidents, colour = factor(lhb))) +
  geom_line()+
  facet_wrap(vars(factor(nature)), scales = "free_y")+
  labs(x="Date", y="Incidents", colour = "Health board")+
  ggthemes::scale_color_colorblind()+
  ggthemes::theme_few()+
  theme(legend.position = "none")

>>>>

data <- data.frame(
  level1 = "Total",
  level2 = c("Central & West", "Central & West", "Central & West", 
             "North", "South & East", "South & East", "South & East"),
  level3 = c("HD", "SB", "PO", "BC", "CV", "CT", "AB")
)
# transform it to a edge list!
edges_level1_2 <- data %>%
  select(level1, level2) %>%
  unique() %>%
  rename(from = level1, to = level2)
edges_level2_3 <- data %>%
  select(level2, level3) %>%
  unique() %>%
  rename(from = level2, to = level3)
edge_list <- rbind(edges_level1_2, edges_level2_3)

mygraph <- igraph::graph_from_data_frame(edge_list)
ggraph::ggraph(mygraph, layout = "dendrogram", circular = FALSE) +
  ggraph::geom_edge_diagonal() +
  ggraph::geom_node_point(color = "#dddddd", size = 10) +
  ggraph::geom_node_text(
    aes(label = c("All country", 
                  "Central & West", "North", "South & East", 
                  "HD", "SB", "PO", "BC", "CV", "CT", "AB"))
  ) +
  theme_void()

@@

```{r}
#| label: tbl-hierarchy
#| tbl-cap: "Number of time series in each level for the hierarchical & grouped structure of attended incidents"
agg_level <- tibble::tribble(
  ~Level, ~`Number of series`,
  "All country", 1,
  "Control", 3,
  "Health board", 7,
  "Priority", 3,
  "Priority * Control", 9,
  "Priority * Health board", 21,
  "Nature of incident", 35,
  "Nature of incident * Control", 105,
  "Nature of incident * Health board", 245,
  "Priority * Nature of incident", 104,
  "Control * Priority * Nature of incident", 306,
  "Control * Health board * Priority * Nature of incident (Bottom level)", 691,
  "Total", 1530
)
knitr::kable(agg_level, booktabs = TRUE, position = "left") %>%
  kable_classic(full_width = FALSE)
```

@@

```{r}
#| label: fig-feature
#| cache: true
#| out.width: "70%"
#| fig.align: center
#| fig-cap: "Time series features of attended incidents across all levels (1530 series)"
incident_gthf <- readr::read_rds(here::here("data/incidents_gt.rds"))
incident_gthf %>%
  features(incident, feat_stl) %>%
  ggplot(aes(x = trend_strength, y = seasonal_strength_week)) +
  geom_point(alpha = 0.5) +
  ggthemes::theme_few() +
  labs(x = "Strength of trend", y = "Strength of weekly seasonality")
```

@@

```{r}
#| label: fig-dataviz
#| cache: true
#| dependson: "fig-feature"
#| out.width: "70%"
#| fig-cap: "Time series of attended incidents at various levels."
#| fig-subcap:
#|   - "Whole country"
#|   - "By control area"
#|   - "By health board and control area"
#|   - "By health board and priority"
#|   - "By nature of incident and health board"
#| layout: [[44,-2, 44], [44,-2, 44], [100]]
p_total <- incident_gthf %>%
  filter(is_aggregated(region) & is_aggregated(lhb) & is_aggregated(category) & is_aggregated(nature)) %>%
  autoplot() +
  labs(x = "Date", y = "Incidents") +
  ggthemes::theme_few()

p_total_control <- incident_gthf %>%
  filter(!is_aggregated(region) & !is_aggregated(lhb) & is_aggregated(category) & is_aggregated(nature)) %>%
  as_tibble() %>%
  select(-nature, -category) %>%
  group_by(date, region) %>%
  summarise(incident = sum(incident), .groups = "drop") %>%
  ggplot(aes(x = date, y = incident, color = factor(region))) +
  geom_line() +
  labs(x = "Date", y = "Incidents", color = "Control") +
  ggthemes::scale_color_colorblind() +
  ggthemes::theme_few() +
  theme(legend.position = "bottom")

p_control <- incident_gthf %>%
  filter(!is_aggregated(region) & !is_aggregated(lhb) & is_aggregated(category) & is_aggregated(nature)) %>%
  as_tibble() %>%
  select(-nature, -category) %>%
  ggplot(aes(x = date, y = incident, color = factor(lhb))) +
  geom_line() +
  facet_wrap(vars(factor(region)), scales = "free_y") +
  labs(x = "Date", y = "Incidents", color = "Health board") +
  ggthemes::scale_color_colorblind() +
  ggthemes::theme_few() +
  theme(legend.position = "bottom")

p_priority <- incident_gthf %>%
  filter(!is_aggregated(region) & !is_aggregated(lhb) & !is_aggregated(category) & is_aggregated(nature)) %>%
  as_tibble() %>%
  select(-nature, -region) %>%
  ggplot(aes(x = date, y = incident, color = factor(lhb))) +
  geom_line() +
  facet_wrap(vars(factor(category)), scales = "free_y") +
  labs(x = "Date", y = "Incidents", color = "Health board") +
  ggthemes::scale_color_colorblind() +
  ggthemes::theme_few() +
  theme(legend.position = "bottom")

@@

p_nature_healthboard <- incident_gthf %>%
  filter(!is_aggregated(region) & !is_aggregated(lhb) & !is_aggregated(category) & !is_aggregated(nature)) %>%
  as_tibble() %>%
  mutate(nature = as.character(nature)) %>%
  filter(nature %in% selected_nature) %>%
  group_by(date, nature, lhb) %>%
  summarise(incident = sum(incident), .groups = "drop") %>%
  ggplot(aes(x = date, y = incident, color = factor(lhb))) +
  geom_line() +
  facet_wrap(vars(factor(nature)), scales = "free_y") +
  labs(x = "Date", y = "Incidents", color = "Health board") +
  ggthemes::scale_color_colorblind() +
  ggthemes::theme_few() +
  theme(legend.position = "none")

### 2022-11-16 manuscript/main.qmd
Cleaner code

```{r}
#| label: setup
#| include: false
library(knitr)
library(tidyverse)
library(lubridate)
library(patchwork)
library(tsibble)
library(kableExtra)
library(fable)
library(ggthemes)
library(readxl)
library(here)
library(tsibble)
library(fable)
```

>>>>

```{r}
#| label: setup
#| include: false
library(fpp3)
library(knitr)
library(kableExtra)
library(ggthemes)
library(patchwork)
#library(ggraph)
#library(igraph)
```

### 2022-11-16 rscript/result/analysing_results.Rmd
Cleaner code

ggplot(rmsse_control_h, aes(x=h,y=rmsse, colour=factor(approach)))+
  geom_point()+
  geom_line()+
  scale_x_continuous(breaks = seq(1,35,1))+
  facet_wrap(vars(level),ncol = 1, scales = "free_y")+
  ggthemes::theme_few()+
  ggthemes::scale_color_colorblind()
```

@@

ggplot(rmsse_hb_h, aes(x=h,y=rmsse, colour=factor(approach)))+
  geom_point()+
  geom_line()+
  scale_x_continuous(breaks = seq(1,35,1))+
  facet_wrap(vars(level),ncol = 2, scales = "free_y")+
  ggthemes::theme_few()+
  ggthemes::scale_color_colorblind()
```

@@

ggplot(rmsse_priority_h, aes(x=h,y=rmsse, colour=factor(approach)))+
  geom_point()+
  geom_line()+
  scale_x_continuous(breaks = seq(1,35,1))+
  facet_wrap(vars(level),ncol = 1, scales = "free_y")+
  ggthemes::theme_few()+
  ggthemes::scale_color_colorblind()
```

>>>>

ggplot(rmsse_control_h, aes(x=h,y=rmsse, color=factor(approach)))+
  geom_point()+
  geom_line()+
  scale_x_continuous(breaks = seq(1,35,1))+
  facet_wrap(vars(level),ncol = 1, scales = "free_y")+
  ggthemes::theme_few()+
  ggthemes::scale_color_colorblind()
```

@@

ggplot(rmsse_hb_h, aes(x=h,y=rmsse, color=factor(approach)))+
  geom_point()+
  geom_line()+
  scale_x_continuous(breaks = seq(1,35,1))+
  facet_wrap(vars(level),ncol = 2, scales = "free_y")+
  ggthemes::theme_few()+
  ggthemes::scale_color_colorblind()
```

@@

ggplot(rmsse_priority_h, aes(x=h,y=rmsse, color=factor(approach)))+
  geom_point()+
  geom_line()+
  scale_x_continuous(breaks = seq(1,35,1))+
  facet_wrap(vars(level),ncol = 1, scales = "free_y")+
  ggthemes::theme_few()+
  ggthemes::scale_color_colorblind()
```
